 Austral Spring Extratropical Southern Hemisphere zonally assymetric circulation

### 2021-06-01 analysis/paper/shceof.Rmd
Agrega referencia de OLS
Closes #44

Linear trends were computed by Ordinary Least Squares and the 95% confidence interval was computed assuming a t-distribution with the appropriate residual degrees of freedom \textcolor{red}{Referencia?}.
The amplitude of the zonal waves was defined through computing the Fourier transform of the spatial field at each latitude circle.
\textcolor{red}{Esto está repetido con lo de arriba o querías referirte a otra cosa}

>>>>

Linear trends were computed by Ordinary Least Squares and the 95% confidence interval was computed assuming a t-distribution with the appropriate residual degrees of freedom [@wilks2011r].
The amplitude of the zonal waves was defined through computing the Fourier transform of the spatial field at each latitude circle.
\textcolor{red}{Esto está repetido con lo de arriba o querías referirte a otra cosa}
